---
output:
  html_document: default
  pdf_document: default
---
Red wine quality dataset exploration
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(plyr)
library(dplyr)
library(GGally)
library(RColorBrewer)
library(memisc)
library(gridExtra)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
rw <- read.csv('winequalityreds.csv')

rw$quality.factor <- factor(rw$quality)
rw$quality.cat <- NA
rw$quality.cat <- ifelse(rw$quality>=7, 'good', NA)
rw$quality.cat <- ifelse(rw$quality<=4, 'bad', rw$quality.cat)
rw$quality.cat <- ifelse(rw$quality==5, 'Average', rw$quality.cat)
rw$quality.cat <- ifelse(rw$quality==6, 'Average', rw$quality.cat)

rw$quality.cat <- factor(rw$quality.cat, levels = c("bad", "Average", "good"))

```


This report explores a dataset containing red wine quality on 11 different variables.

# Univariate Plots Section


The dataset consists of 13 variables of 1599 observations.

```{r echo=FALSE, Univariate_Plots}
str(rw)
summary(rw)

```

```{r echo=FALSE, message=FALSE, warning=FALSE }
qplot(x=quality,data=rw,binwidth = 1)+
  scale_x_continuous(breaks = seq(0,10,1))
summary(rw$quality)
table(rw$'quality')

```

It looks like most wines were rated average between 5 and 6 with a mean of 5.6 
and median 6. No wine was rated 1 and none was given 9 or 10. A very small 
percentage is rated 8 and even a smaller percentage is rated 3. It would be 
interesting to compare qualities of these two categories (perhaps 3 vs 8)
to see if there is stark difference in specific attributes.

For now, let's look at other variables to see what we can find.

```{r echo=FALSE, message=FALSE}
by_quality<-group_by(rw,quality)
wine_by_quality<-summarise(by_quality,
                           mean_alc = mean(alcohol),
                           median_alc = median(alcohol),
                           min_alc = min(alcohol),
                           max_alc = max(alcohol),
                           n = n())
head(wine_by_quality)
```

Mean alcohol content in highly rated wines is much higher than wines rated low.


```{r echo=FALSE, message=FALSE}
qplot(x=alcohol, data=rw,binwidth=0.5)+
  scale_x_continuous(breaks= seq(0.5,16,0.5))

```

We can see that majority of the wines had an alcohol content between 9.5 and 10 
which is interesting because based on common knowledge most wines have alcohol 
content of 13.5% alc/vol. This indicates most were low in alcohol content which 
could indicate why most have not been rated very high.

Fixed acidity shows a normal plot.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=fixed.acidity,data=rw,binwidth=0.5)
```

Let's look at volatile acidity next since a high concentration of that will 
result in a vinegary taste in wines and in theory affects quality.


```{r echo=FALSE, message=FALSE, warning=FALSE}
wine_by_acidity<-summarise(by_quality,
                           mean_acid = mean(volatile.acidity),
                           median_acid = median(volatile.acidity),
                           min_acid = min(volatile.acidity),
                           max_acid = max(volatile.acidity),
                           n = n())
head(wine_by_acidity)
```

We can see that mean and median acidity levels decrease as quality ratings increase.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=volatile.acidity, data=rw, binwidth =0.1)
summary(rw$volatile.acidity)

```

We do see some that are highly acidic > 1 and some >1.5  but for the most part 
they lie around 0.5 gm/l

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=residual.sugar, data=rw,binwidth=0.1)+
  scale_x_continuous(breaks=seq(0,16,0.5))
summary(rw$residual.sugar)
```

We have a lot of wines with fairly low sugar content between 1.5 and 2.5 with 
2 gm/liter as being the most common. We don't seem to have any wines considered
"very sweet" (>45g/l) since the sugar content ranges from 0.9 to 15.5 gm/liter 
only. Let's do a log transform to normalize the data. 

```{r echo=FALSE, message=FALSE}

qplot(x=residual.sugar,data=rw,binwidth=0.1)+
  scale_x_log10()
```

Also, We do notice a small batch of wines with sugar content >8 but they are 
very small in number. Let's zoom in to take a closer look.

```{r echo=FALSE, message=FALSE, warning=FALSE, residualsugar}
qplot(x=residual.sugar, fill = quality.cat, data=rw,binwidth=0.1)+
  scale_x_continuous(limits =c(7,16),breaks=seq(7,16,2))+
  facet_wrap(~quality.cat)
```

2 wines rated good have low sugar content and the one rated bad has high sugar.
But, we do have wines rated average with sugar content varying across the spectrum 
and is a definite candidate for a bivariate analysis.
Next, let's look at a few other variables.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=density, data=rw,binwidth=0.0001)
```

Most don't differ too much in density. Since density is affected by alcohol and 
sugar content, we'll table this for now.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=citric.acid, data=rw,binwidth = 0.01)
```

We see almost a bimodal distribution. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=citric.acid, data=rw,binwidth = 0.01)+
  scale_y_continuous(breaks = seq(0,120,10))+
  facet_wrap(~quality.cat)
```

Majority of wines have a varying amount of citric acid in tiny amounts. We find
a lot of wines having little to no citric acid. More than 110 wines have no 
citric acid and have been rated average.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=chlorides, data=rw,binwidth =0.01)
summary(rw$chlorides)
```

Majority appear to have low quantities of chloride mostly between possibly 0.01 
and less than 0.2. Let's zoom in on these ignoring the tail for now.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=chlorides, data=rw,binwidth =0.005,xlim=c(0,0.2))
  
```

Quite apparent that most wines have chloride values between 0.05 and 0.1. Now 
let's look at the tail.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=chlorides, data=rw,binwidth =0.005,xlim=c(0.2,0.65))+
  facet_wrap(~quality.cat)
```

We see a handful of wines with a high chloride aka salt content. We have most of
these rated average and just a couple rated good. Therefore, it looks like though 
high chloride content doesn't contribute to good wines, it doesn't always 
lead to bad wines either.


Let's look at free sulphur dioxide since SO2 affects oxidation which in turn is 
known to affect quality of wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=free.sulfur.dioxide, data=rw,binwidth=10)+
  scale_x_continuous(breaks = seq(0,72,10))
  
summary(rw$free.sulfur.dioxide)
```

It looks like we do have wines with >50 mg/l of SO2. The dataset explains that with concentrations higher than that, it affects the taste and smell of wine. Common 
knowledge does indicate SO2 has a foul smelling odor so let's investigate this.

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=free.sulfur.dioxide, data=rw,binwidth = 5)+
  scale_x_continuous(limits=c(50,72))+
  facet_wrap(~quality.cat)+
  ggtitle('Quality of wines with high concentration of SO2')


```

We have about 6 wines with a high free SO2 content. Surprisingly, none of them were
rated bad!

Let's then take a look at total SO2 and apply log transformation to get a normal 
curve. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=total.sulfur.dioxide, data=rw,binwidth=10)

qplot(x=total.sulfur.dioxide, data=rw,binwidth = 0.1)+scale_x_log10()
```

We note that a small number of wines have total SO2 content around 289 but let's
focus on the high tail. At 30 mg/l, close to 300 wines seem to have that amount.


```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=total.sulfur.dioxide, data=rw,binwidth=10)+
  scale_x_continuous(breaks=seq(0,190,20),limits=c(50,190))+
  facet_wrap(~quality.cat)
 

summary(rw$total.sulfur.dioxide)
```

Looking at pH and sulfates

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=pH,data=rw,binwidth=.1)+
  scale_x_continuous(breaks=seq(0,4.5,0.1))
summary(rw$pH)
```

Bulk of the wines have a pH between 3.2 and 3.5 which agrees with known fact
that most wines are fairly acidic with range between 3-4 on a pH scale. We do
see one wine close at3.9 and another wine as low as 2.7.Both were rated "bad". 

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=pH,data=rw,binwidth=.1)+
  scale_x_continuous(breaks=seq(2,4.5,0.2))+
  facet_wrap(~quality.cat,scales="free_y")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=sulphates,data=rw,binwidth =.1)
summary(rw$sulphates)
```

suphates contributes to SO2 gas which prevents oxidation and also acts as 
antimicrobial according to given information. The concentration varies from 0.3
to 1.4 for most wines. We do see some high concentrations of around 2 in some 
wines. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
qplot(x=sulphates,data=rw,binwidth =.1)+facet_wrap(~quality.cat)
```


# Univariate Analysis

### What is the structure of your dataset?

There are 1599 red wines that have been rated on a scale from 1 to 10, 10 being 
the best and 1 being the worst. 11 different input variables (Ex.pH, alcohol 
content etc) have been tested for and the output variable (quality) has been measured. 
All the input variables are numeric while output variable is int.

Other observations:
1. No wines have been given either a very poor rating (1) or very excellent rating 
(9 or 10)
2. Average rating of the wines is 5.6 with a median of 6. Least rating is 3 and
max rating is 8.

### What is/are the main feature(s) of interest in your dataset?
Based on common knowledge, factors such as sugar, alcohol and acidity
affect the taste and quality. But it would be interesting to plot a scatter plot 
matrix to understand effect of other variables as well as between input variables.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

I think sulphates, pH and sulphur di oxide also affect quality.

### Did you create any new variables from existing variables in the dataset?

Yes. Since quality is numeric, I changed it to a qualitative variable - a factor
variable named quality.factor for ease of analysis
```{r}
rw$quality.factor <- factor(rw$quality)
rw$quality.cat <- NA
rw$quality.cat <- ifelse(rw$quality>=7, 'good', NA)
rw$quality.cat <- ifelse(rw$quality<=4, 'bad', rw$quality.cat)
rw$quality.cat <- ifelse(rw$quality==5, 'Average', rw$quality.cat)
rw$quality.cat <- ifelse(rw$quality==6, 'Average', rw$quality.cat)

rw$quality.cat <- factor(rw$quality.cat, levels = c("bad", "Average", "good"))
```



### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

residual sugar and total sulfur di oxide was not normal data so I transformed it 
using the log function in order to normalize the data.

# Bivariate Plots Section


Drawing a sample of 1000, let's look at ggpairs plots.

```{r echo=FALSE, fig.width=12, fig.height=9, Bivariate_Plots}
set.seed(1001)
rw_subs<-rw[sample(1:length(rw$quality),1000),]
ggpairs(rw_subs,lower = list(continuous = wrap("points", shape = I('.'))), 
        upper = list(combo = wrap("cor", outlier.shape = I('.'), size = 1)),columns = 2:13)+
        theme(axis.text = element_text(size = 1),
              panel.grid.minor = element_blank())


```

With respect to quality, there's a moderate positive correlation to alcohol 
content (0.504) and a weak positive correlation to citric acid (.223) and sulphates 
concentration (.267).

There is a weak negative correlation of quality to volatile acid (-.377) and 
total sulphur di oxide (-.196). 

Surprised to learn pH is not highly correlated to quality (-0.068) and neither
is chlorides (-0.129)

##Relationship between variables##
Interestingly, there is strong positive correlation between fixed acidity and 
density (.658) as well as between citric acid and fixed acidity (.665). The latter
maybe just a result of acidic content measurement since citric acid content would
contribute to the acidic content. The former would be interesting to explore.
Fixed acidity is highly positively correlated to density and highly negatively
correlated to pH as shown.

```{r echo=FALSE, message=FALSE, warning=FALSE}
d1<-ggplot(aes(x=fixed.acidity, y= density),data=rw)+
  geom_point(alpha=1/7, size =1, position='jitter')+
  geom_smooth(method='lm')
d2<-ggplot(aes(x=fixed.acidity, y= pH),data=rw)+
  geom_point(alpha=1/7, size =1, position='jitter')+
  geom_smooth(method='lm')
grid.arrange(d1,d2)
```

Let us analyze the quantitativeness of the variables using boxplots.

```{r echo=FALSE, message=FALSE, warning=FALSE}
b1<-ggplot(aes(x=quality.cat, y= alcohol),data=rw)+
  geom_boxplot(alpha = 1/20,color = 'blue')+
  geom_jitter( alpha = 1/20)+
   stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
b2<-ggplot(aes(x=quality.cat, y= citric.acid),data=rw)+
  geom_boxplot(alpha = 1/20,color = 'blue')+
  geom_jitter( alpha = 1/20)+
     stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
b3<-ggplot(aes(x=quality.cat, y= sulphates),data=rw)+
  geom_boxplot(alpha = 1/50,color = 'blue')+
  geom_jitter( alpha = 1/50)+
     stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
b4<-ggplot(aes(x=quality.cat, y= volatile.acidity),data=rw)+
  geom_boxplot(alpha = 1/20,color = 'blue')+
  geom_jitter( alpha = 1/20)+
     stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)

b6<-ggplot(aes(x=quality.cat, y= density),data=rw)+
  geom_boxplot(alpha = 1/20,color = 'blue')+
  geom_jitter( alpha = 1/20)+
    stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
b7<-ggplot(aes(x=quality.cat, y= pH),data=rw)+
  geom_boxplot(alpha = 1/30,color = 'blue')+
  geom_jitter( alpha = 1/30)+
      stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 8, 
               size = 4)
  
grid.arrange(b1,b2,b3,b4,b6,b7,ncol=3)

```

We can see box plots of density and pH are almost mirror images of each other.
Let's further explore scatter plots of just these variables of interest.

We see most wines rated bad are low in alcohol and most wines rated good are 
high in alcohol content. But, we also see wines with high alcohol content rated 
average as shown by the outliers. Therefore, clearly some other factors also 
contribute to quality.




Regards to total sulphur dioxide content, most rated average have low levels. 
Therefore it is likely that this variable was not a major contributing factor affecting
quality. Unless we have more data (i.e more wines rated bad and good in the data set)
and we are able to analyze So2 content there, we can table this.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=total.sulfur.dioxide, y= quality),data=rw)+
  geom_boxplot(alpha = .5,color = 'blue')+
  geom_jitter( alpha = .3)+
  stat_summary(fun.y = "mean", 
               geom = "point", 
               color = "red", 
               shape = 4, 
               size = 2)
```

Let's further explore the relationship between variables. I think pH and acidity
having a negative correlation is expected given that pH is a measure of acidic content.

# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?


We see most wines rated bad are low in alcohol and most wines rated good are 
high in alcohol content. But, we also see wines with high alcohol content rated 
average as shown by the outliers. Similar was the case with citric acid where 
presence in fair amounts is good but a lot of it doesn't necessarily mean good 
wine and the absence of it also doesn't imply bad wine quality. Therefore, 
clearly a lot of factors play together into determining quality.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

Based on common knowledge and what was a given information, I assumed a high 
concentration of sulfur di oxide (>50 mg/l) would lead to bad wines but that was
not so when I drew up the plot of free so2 vs quality.

### What was the strongest relationship you found?

The strongest relationship (for quality) was definitely to the alcohol content.
For wines with high alcohol content, there were other factors that played into 
determining quality but there were no wines rated good that were low in alcohol 
content which strengthened the results.

# Multivariate Plots Section


```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=alcohol, y= citric.acid),data=rw)+
  geom_point(aes(color=quality.cat),stat='summary',fun.y=mean)+
  geom_smooth(method ='lm')
  ggtitle('citric acid vs alcohol by quality')

```

Looking at 1st and 3rd plots, wines rated good generally have higher citric acid 
content,implying fresher wines and some that had low citric acid content but rated 
higher, had high alcohol content. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=volatile.acidity, y= log(total.sulfur.dioxide),colour = quality.cat),data=rw)+
  geom_point(alpha =1/5)+
  geom_smooth(method = "lm", se = FALSE,size=1)  



```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = sulphates, y = alcohol, colour = quality.cat), 
       data = rw) + 
  geom_point(alpha=1/2) +
  geom_smooth(method = "lm", se = FALSE,size=1)  +
  scale_color_brewer(type = 'div', palette="Set1") 
 
```

## Regression model

```{r echo=FALSE, message=FALSE, warning=FALSE}
m1<-lm(I(rw$quality)~I(rw$alcohol),data=rw)
m2<-update(m1,~.+rw$citric.acid)
m3<-update(m2,~.+rw$sulphates)
m4<-update(m3,~.+rw$volatile.acidity)

mtable(m1,m2,m3,m4,sdigits=3)

#library(corrplot)
#M <- cor(rw)
#corrplot(M, method="circle")
  
```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

I think it was understanding the relationship between alcohol and citric acid that
both contributed to good quality wines. Also, learning that although a good 
concentration of both is important for a good quality, too much of it doesn't 
necesssarily imply that you would get a good wine.

### Were there any interesting or surprising interactions between features?

The interaction between sulphates and alcohol content was interesting. Wines 
rated bad were mostly clustered around the bottom left with low concentration of 
sulphates and on the right were mostly rated average and good with most of the 
good wines clusterted on the top right with high concentrations of both.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

Yes, I created a regression model to predict the quality of wines based on selected
independent variables in the dataset. 

The model explains about 34% of cases with
the highest R quared when 4 variables (alcohol, citric acid, sulphates and volatile acidity 
) are included. 

There are some limitations of this model given that ggpairs is based off of a sample
of the dataset and any additional data might alter the results. Also, this dataset 
is for nearly 1600 wines with very few wines on either side of the quality spectrum 
so any additions to this especially adding to very low quality (3) or very high quality
(8 or above) is likely to affect the results.


# Final Plots and Summary


### Plot One

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x = sulphates, y = alcohol, colour = quality.cat), 
       data = rw) + 
  geom_point(alpha=1/2) +
  geom_smooth(method = "lm", se = FALSE,size=1)  +
  scale_color_brewer(type = 'div', palette="Set1") +
  ggtitle('Interaction between sulphates and alcohol content affecting quality')+
  xlab('sulphates [g/dm3]')+
  ylab ('alcohol [% by volume]')


```

### Description One

We can see how wines rated bad(red) are around the bottom left and wines rated
good are clustered around the top right (green). We have average wines clustered 
around the middle. This provides an explanation to an extent between the interaction 
between some of the variables that affect quality.

### Plot Two

```{r echo=FALSE, message=FALSE, warning=FALSE}
b1<-ggplot(aes(x=quality.cat, y= alcohol),data=rw)+
  geom_boxplot()+
  xlab('Quality')+
  ylab('alcohol [%]')+
  stat_summary(fun.y=mean,geom='point',shape=4)
b2<-ggplot(aes(x=quality.cat, y= citric.acid),data=rw)+
  geom_boxplot()+
  xlab('Quality')+
  ylab('citric acid [g/dm^3]')+
  stat_summary(fun.y=mean,geom='point',shape=4)
  theme(axis.text.x = element_text(size=5), axis.text.y = element_text(size=12))
b3<-ggplot(aes(x=quality.cat, y= sulphates),data=rw)+
  geom_boxplot()+
  xlab('Quality')+
  ylab('sulphates [g/dm^3]')+
  stat_summary(fun.y=mean,geom='point',shape=4)
b4<-ggplot(aes(x=quality.cat, y= volatile.acidity),data=rw)+
  geom_boxplot()+
  xlab('Quality')+
  ylab('volatile acidity[g/dm^3]')+
  stat_summary(fun.y=mean,geom='point',shape=4)
b6<-ggplot(aes(x=quality.cat, y= density),data=rw)+
  geom_boxplot()+
  xlab('Quality')+
  ylab('density [g/cm^3]')+
  stat_summary(fun.y=mean,geom='point',shape=4)
b7<-ggplot(aes(x=quality.cat, y= pH),data=rw)+
  geom_boxplot()+
  xlab('Quality')+
  ylab('pH')+
  stat_summary(fun.y=mean,geom='point',shape=4)
grid.arrange(b1,b2,b3,b4,b6,b7,ncol=3, top = 'Box plots of key variables')
```

### Description Two

The box plots clearly depict the variation of each of the factors with quality.
We can see how the mean moves higher with increasing quality for variables - alcohol,
citric acid and sulphates. We can also see the reverse scenario for variables
such as volatile acidity and density.

### Plot Three

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(x=alcohol, y= citric.acid),data=rw)+
  geom_point(aes(color=quality.cat),stat='summary',fun.y=mean)+
  geom_smooth(method = "lm", se = FALSE,size=1)  +
  stat_ellipse(linetype=2)+
  xlab('alcohol[%]')+
  ylab('citric acid [g/dm^3]')+
  ggtitle('citric acid vs alcohol by quality')
```

### Description Three

Pitting acid against alcohol, we can see good wines (blue) clustered mostly on top
of the plot, average in the middle (green) and bad wines (in red) clustered around
the bottom. It is evident citric acid, results in fresh tasting wines and therefore,
better quality wines. However, too much of it doesn't necessarily imply good wines
as can be seen from a green point on the top right with both high citric acid and high alcohol content.

We see a lot of good wines centered in the middle (alcohol content between 10 and 13)
but on the left, where alcohol content is low, we see mostly wines rated bad and 
average.
Also, on the right area of the plot where alcohol content is high, we mostly see
good and average wines but not bad wines.
Definitely, we can derive that alcohol content is a good predictor of quality of 
wine.
------

# Reflection

It was interesting to see some affirmations for some assumptions such as alcohol 
content and citric acid yielding good quality wines. It was surprising to learn
how some variables such as sugar not really affecting quality as much. Perhaps there is a lot of difference between what we know as a fact versus what we perceive. 

Since there was little data on both good and bad wines but more on average wines,
it was hard to delineate a pattern from such limited information. 

Also, the quality of these wines have been based on what can be measured quantitavely
but other factors such as color and smell which are also huge determining factors
in deciding quality would be interesting to analyze.

# References

https://s3.amazonaws.com/content.udacity-data.com/courses/ud651/diamondsExample_2016-05.html
https://discussions.udacity.com/t/ggpairs-function/287231/11
https://rpubs.com/jeknov/redwine
https://discussions.udacity.com/t/spoiler-code-need-helping-knitting-my-rmd-file-into-an-html-doc/294489




